---
title: "GGPlot"
author: "Duy Trinh"
date: "January 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(RColorBrewer)
```

TABLE WAY

Percentage | Male | Female
-----------|------|--------
First class|10    | 12
Second class| 12 | 123

COOL KIDS WAY


# Problem 3
## e/ 

```{r}
nsims <- 1000
size <- 200
beta <- c(0,5)
betahat <- NA
var <- NA
se <- NA

x <- cbind(rep(1,size), rnorm(size, mean=1, sd=1)) # Generate vector of 200 x from standard normal distribution

for (i in 1:nsims){
  y <- x%*%beta + rnorm(size, mean=0, sd=1)
  reg.sim <- lm(y~x)
  betahat[i] <- summary(reg.sim)$coef[2,1]
  se[i] <- summary(reg.sim)$coef[2,2]
  var[i] <- se[i]^2
}
```

## h/

Generate the plot dataframe

```{r}
simplot <- data.frame(betahat, se)
simplot$overlap <- ifelse(betahat-1.96*se <= beta[2] & betahat+1.96*se >= beta[2], "Yes","No")
```

One can think of a ggplot as an object with multiple layers. The function `ggplot()` creates a base layer that contains the data and default graphical options; each succeeding command, followed by a + sign, adds another layer to the graph.

For example, this command adds the points. Note how I include an option `(color="black")`to override the default.
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black")
```
Now I will add the error bars and highlight the true beta
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed")
```
Looks ugly. How about I resize it a little bit?
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed") +
  scale_y_continuous(limits=c(4.5,5.5)) +
  coord_fixed(400)
```
Now I'll add some titles and labels to it
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed") +
  scale_y_continuous(limits=c(4.5,5.5)) +
  coord_fixed(400) +
  theme(legend.position="bottom") +
  labs(title ="Confidence intervals for 1000 simulations", x = "Simulation", y = "Simulated beta")
```
There are many, many, *many* ways to customize the plot. Explore away!
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed") +
  scale_y_continuous(limits=c(4.5,5.5)) +
  coord_fixed(400) +
  theme(plot.title=element_text(size=18,face="bold",hjust=0.5), legend.position="bottom") +
  theme(axis.ticks = element_blank(), legend.title = element_blank()) +
  labs(title ="Confidence intervals for 1000 simulations", x = "Simulation", y = "Simulated beta")
```
With a couple of additional packages such as `RColorBrewer` and `ggthemes`, we can create wonders at will(or monstrosities, if you so wish)
```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed") +
  scale_y_continuous(limits=c(4.5,5.5)) +
  coord_fixed(400) +
  theme(plot.title=element_text(size=18,face="bold",hjust=0.5), legend.position="bottom") +
  theme(axis.ticks = element_blank(), legend.title = element_blank()) +
  scale_color_brewer(palette="Dark2") + 
  labs(title ="Confidence intervals for 1000 simulations", x = "Simulation", y = "Simulated beta")
```

```{r}
ggplot(simplot, aes(x=1:nsims, y=betahat, color=overlap)) +
  geom_point(color="black") +
  geom_errorbar(aes(ymin = betahat-1.96*se, ymax = betahat+1.96*se)) +
  geom_hline(yintercept=5, size=1, linetype = "dashed") +
  scale_y_continuous(limits=c(4.5,5.5)) +
  coord_fixed(400) +
  theme(plot.title=element_text(size=18,face="bold",hjust=0.5), legend.position="bottom") +
  theme(axis.ticks = element_blank(), legend.title = element_blank()) +
  theme_excel() + scale_color_excel() +
  labs(title ="Confidence intervals for 1000 simulations", x = "Simulation", y = "Simulated beta")
```